\documentclass[a4paper,10pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{amsmath} % Prevent math mode issues
\pagestyle{fancy}
\fancyhf{}
\rhead{Harmohit Singh}
\lhead{Resume}
\rfoot{\thepage}

\titleformat{\section}{\bfseries\Large}{}{0em}{}[\titlerule]
\titleformat{\subsection}{\bfseries}{}{0em}{}

\begin{document}

\begin{center}
    \textbf{\LARGE Harmohit Singh} \\
    \vspace{0.2em}
    \textbf{\input{../assets/other/job_title.tex}} \\
    \href{https://linkedin.com/in/harmohit-singh}{linkedin.com/in/harmohit-singh} \quad \href{mailto:harmohitsingh@hotmail.com}{harmohitsingh@hotmail.com} \quad +91-8527744300
\end{center}

\section*{Summary}
\input{../assets/other/summary.tex}

\section*{Skills}
\textbf{Technologies:} \input{../assets/other/technologies.tex} \\
\textbf{Other skills:} \input{../assets/other/other_skills.tex}

\section*{Education}
\textbf{B.Tech. in Electronics}, PEC University of Technology \\
\textit{Jul 2008 – May 2012, Chandigarh, India}

\section*{Professional Experience}

\subsection*{CoreOps — Enterprise AI Head}
\textit{Mar 2025 – Present, Noida, India (Hybrid)} \\
\\
Led ML and Gen AI initiatives across Central AI and Ads ML teams, designing scalable ML pipelines and mentoring a team of ~5 data scientists. Spearheaded end-to-end solutioning, development, deployment, and continuous optimization of ML pipelines and Gen AI solutions.
\begin{itemize}
    \item Optimized the ML pipeline in the Ads ML team, enhancing accuracy and efficiency. Upgraded the data pipeline by adding features and transitioned the algorithm from tree-based models to neural networks, driving an average \textbf{~20\% increase in ad conversion rates} across app properties
    \item Successfully delivered projects predicting customer click behavior and churn (used XGBoost and ANN), enhancing business decision-making.
    \item Established A/B testing pipeline and sustained model improvement, achieving a consistent \textbf{lift of ~15\%}
    \item Built AI solutions, such as a natural language based BI tool enabling rapid decision-making for non-technical users, and voice-based solutions enhancing customer support efficiency. These solutions \textbf{resulted in a 90\% reduction in man-hours and a 60\% decrease in employee costs}
    \item Implemented cost-saving measures and optimized various processes using data engineering across multiple projects, resulting in a \textbf{90\% reduction} in compute resources
    \item Engaged in the decision-making and implementation of app modifications to \textbf{enhance traffic and engagement} across multiple businesses. Utilized data science and analytics (with A/B testing) to drive data-informed decisions
\end{itemize}

\subsection*{Paytm — General Manager - Data Science}
\textit{Apr 2023 – Mar 2025, Gurugram, India (Hybrid)} \\
\\
Led ML and Gen AI initiatives across Central AI and Ads ML teams, designing scalable ML pipelines and mentoring a team of ~5 data scientists. Spearheaded end-to-end solutioning, development, deployment, and continuous optimization of ML pipelines and Gen AI solutions.
\begin{itemize}
    \item Optimized the ML pipeline in the Ads ML team, enhancing accuracy and efficiency. Upgraded the data pipeline by adding features and transitioned the algorithm from tree-based models to neural networks, driving an average \textbf{~20\% increase in ad conversion rates} across app properties
    \item Successfully delivered projects predicting customer click behavior and churn (used XGBoost and ANN), enhancing business decision-making.
    \item Established A/B testing pipeline and sustained model improvement, achieving a consistent \textbf{lift of ~15\%}
    \item Built AI solutions, such as a natural language based BI tool enabling rapid decision-making for non-technical users, and voice-based solutions enhancing customer support efficiency. These solutions \textbf{resulted in a 90\% reduction in man-hours and a 60\% decrease in employee costs}
    \item Implemented cost-saving measures and optimized various processes using data engineering across multiple projects, resulting in a \textbf{90\% reduction} in compute resources
    \item Engaged in the decision-making and implementation of app modifications to \textbf{enhance traffic and engagement} across multiple businesses. Utilized data science and analytics (with A/B testing) to drive data-informed decisions
\end{itemize}

\subsection*{EXL Services — AVP - Data Science}
\textit{Sep 2021 – Apr 2023, Gurugram, India (Remote)} \\
\\
Developed and deployed machine learning solutions addressing attrition, retention, and cross-selling challenges, while managing end-to-end stakeholder engagement, including strategic leadership, delivery oversight, team development, and business relations. Led a multidisciplinary team of data scientists, analysts, data engineers, and project managers.
\begin{itemize}
    \item Implemented a propensity model (using XGBoost) for call routing, \textbf{identifying at-risk customers and directing them to specialized retention teams}. This approach reduced call transfers and handle time while enhancing overall call ratings. Achieved \textbf{lift of ~10\%}
    \item Migrated ML model scoring and training workflows to a custom AWS-based platform. Implemented ML pipeline for model retraining, evaluation, and scoring. This \textbf{reduced infrastructure costs to 1/8th} by eliminating licensing fees
    \item Oversaw \textbf{team and revenue growth}, business and relationship development, and client/stakeholder management. During my tenure, \textbf{team size grew by approximately 20\% and revenue increased by about 24\%}
\end{itemize}

\subsection*{Epsilon — Senior Data Scientist}
\textit{Dec 2018 – Aug 2021, Bengaluru, India}
\\
\\
Directed the full machine learning lifecycle, from stakeholder engagement to solution deployment and productionization. Oversaw and supported a team of developers and data scientists through mentoring and management.
\begin{itemize}
    \item Designed and deployed multiple \textbf{ML models (XGBoost and ANN) to develop recommendation engines} for diverse clients, including hotel chains, retailers, and consumer finance institutions. Achieved notable campaign success, with \textbf{~300\% revenue growth, 7\% increase in open rates, and 21\% improvement in click through rates}
    \item Utilized \textbf{advanced algorithms (ANN, NN embeddings, XGBoost) and champion-challenger approach} to build \textbf{ML pipelines}, automating model refresh, enhancement, deployment, and performance monitoring
    \item Spearheaded \textbf{internal initiatives, building code pipelines} and adding features for streamlined modeling and analysis, saving team's time and enhancing capabilities
\end{itemize}

\subsection*{Transorg Analytics — Data Science Lead}
\textit{Oct 2014 – Nov 2018, Mumbai, India}
\\
\\
Worked as a Data Scientist/Analytics Consultant and managed a team of data scientists to assist client in analytics-based business solutions.
\begin{itemize}
    \item Established big data architecture for a payments bank, enabling organization-wide dashboards and advanced machine learning applications. \textbf{Automated the whole process with PySpark and bash scripts}. Implemented targeted campaigning with a 360-degree customer view, resulting in a \textbf{response rate increase of ~150\%}
    \item Worked with an AMC to develop a redemption prediction model (\textbf{~11\% error}) and created a model for targeted product offerings and upgrades for a credit card company, \textbf{contributing to revenue growth of ~\$70 million}
\end{itemize}

\subsection*{AbsolutData Analytics — Business Analyst} 
\textit{Sep 2012 – Feb 2014, Gurugram, India}
\\
\begin{itemize}
    \item Utilized predictive analytics to identify potential customers for a fashion brand in specific USA regions
    \item Conducted trend analysis in the travel and online booking sector to inform product development and marketing strategies
\end{itemize}

\end{document}
